DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-05 paper/appendix.tex
Add draft training section to appendix
Also made some minor changes.

>>>>

\subsection{DNN Training and Testing}
We train a neural network model across a set of 30 completed runs on 
the track seen in Figure~\ref{fig:track} by a human pilot. Half of 
the runs saw the car driving one way along the track, while the 
remaining half were of the car driving in the opposite direction on 
the track. In total, we collected 2,556 frames for training and 2,609 
frames for validation. In each training step, we use a batch size of 
100 frames which are used to further develop the model. We do this 
across 2,000 training steps. When a model was trained with the 
aformentioned data, the training loss was 0.0188 and the validation 
loss was 0.0132.

\begin{figure}[t]
  \centering
  \includegraphics[width=.55\textwidth]{figs/TrainingLoss}
  \caption{DeepPicar's control loop processing times over 1000 input 
image frames.}
  \label{fig:modelloss}
\end{figure}

We also trained models where center frames (where the car was going 
straight) and curve frames (where the car was turning) were equally 
selected in each batch, and were pleasantly surprised at the change 
in the car's performance. With the second model, the car displayed a 
greater ability to stay in the center of the track (on the white 
tape). This was problematic, however, as the loss values changed with 
the training loss being 0.009 and the validation loss becoming 
0.0869, indicating that overfitting had become a problem. We believe, 
though, that this can be rectified through the collection of 
additional data for training and validation.

### 2017-10-05 paper/background.tex
Add draft training section to appendix
Also made some minor changes.

Using deep nueral networks involves two distinct
phases~\cite{NVIDIA2015}. The first
phase is \emph{training} during which the weights of the network is
incrementally updated by backpropating errors it sees from the
training examples. Once the network is trained---i.e., the weights of
the network minimize errors in the training examples---the next phase
is \emph{inferencing} during which unseen data is fed to the network
as input to produce predicted output (e.g., predicted image
classification). In general, the training phase is most compute
intensive and requires high throughput, which is generally not
available on embedded platforms. The inferencing phase, on the
other hand, is relatively less compute intensive and latency becomes
as important, if not more, as compute throughput because many
use-cases have strict real-time requirements (e.g., search query
latency).

>>>>

Using deep neural networks involves two distinct
phases~\cite{NVIDIA2015}. The first
phase is \emph{training} during which the weights of the network is
incrementally updated by backpropagating errors it sees from the
training examples. Once the network is trained---i.e., the weights of
the network minimize errors in the training examples---the next phase
is \emph{inferencing} during which unseen data is fed to the network
as input to produce predicted output (e.g., predicted image
classification). In general, the training phase is most compute
intensive and requires high throughput, which is generally not
available on embedded platforms. The inferencing phase, on the
other hand, is relatively less compute intensive and latency becomes
as important, if not more, as compute throughput because many
use-cases have strict real-time requirements (e.g., search query
latency).

### 2017-10-05 paper/intro.tex
Add draft training section to appendix
Also made some minor changes.

% broad context:
% - advance in ai sparked interests in the robotics application, such as
%   self-driving cars.
% - in particular, deep neural network models are increasingly used
%   for perception and control of a vehicle. say. AI workloads.
%
%
Autonomous cars have been a topic of increasing interest in recent
years as many companies are actively developing related hardware
and software technologies toward fully autonomous driving capability without
any human intervention. Deep neural networks (DNNs) have been
sucessfully applied in various perception and control tasks in
recent years, and they are important workloads for autonomous vehicles
as well. For example, Tesla Model S was known to use a specialized
chip (MobileEye EyeQ), which uses a deep neural network for vision-based
real-time obstacle detection and avoidance. More recently, researchers
are investigating DNN based end-to-end control of
cars~\cite{Bojarski2016} and other robots. It is expected that more
DNN based Artifical Intelligence workloads may be used in future
autonomous vehicles.

% big problem
Executing these AI workloads on a embedded computing platform that can
be used in a car poses several additional challenges. First, many AI
workloads in vehicles are computationally demanding and have strict
real-time requirements. For example, latency in a vision-based object
detection task may directly linked to safety of the vehicle. This
requires a high computing capacity as well as means to guaranteeing
the timings. On the other hand, the computing hardware platform must
also satisfy cost, size, weight, and power constraints, which require
highly efficient computing platform. These two conflicting
requirements  complicate the platform selection process as observed in
~\cite{Otterness2017}, which evaluated vision workloads on
NVIDIA's Tegra TX1 platform.

>>>>

% broad context:
% - advance in ai sparked interests in the robotics application, such as
%   self-driving cars.
% - in particular, deep neural network models are increasingly used
%   for perception and control of a vehicle. say. AI workloads.
%
%
Autonomous cars have been a topic of increasing interest in recent
years as many companies are actively developing related hardware
and software technologies toward fully autonomous driving capability without
any human intervention. Deep neural networks (DNNs) have been
successfully applied in various perception and control tasks in
recent years, and they are important workloads for autonomous vehicles
as well. For example, Tesla Model S was known to use a specialized
chip (MobileEye EyeQ), which uses a deep neural network for vision-based
real-time obstacle detection and avoidance. More recently, researchers
are investigating DNN based end-to-end control of
cars~\cite{Bojarski2016} and other robots. It is expected that more
DNN based Artificial Intelligence workloads may be used in future
autonomous vehicles.

% big problem
Executing these AI workloads on an embedded computing platform that can
be used in a car poses several additional challenges. First, many AI
workloads in vehicles are computationally demanding and have strict
real-time requirements. For example, latency in a vision-based object
detection task may be directly linked to safety of the vehicle. This
requires a high computing capacity as well as means to guaranteeing
the timings. On the other hand, the computing hardware platform must
also satisfy cost, size, weight, and power constraints, which require
highly efficient computing platform. These two conflicting
requirements  complicate the platform selection process as observed in
~\cite{Otterness2017}, which evaluated vision workloads on
NVIDIA's Tegra TX1 platform.
